---
title: "Final Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

read data into R
```{r}
data <-read.csv("C:/Users/duyen/Dropbox/Grad Students/Grad - Duyen/Current classes/PSYC259 R Course/raw cut.csv", header=TRUE)
```

```{r}
names(data)
summary(data)
```


Variable used in this dataset:
RacTot_12 = total racism
xpromotionofmistrust_12 = promotion of mistrust
xmisttrusttot_C = medical mistrust during COVID
ChildSex = child gender
ChildRace_Final = child race 
incometopovertyratio_12 = family socioeconomic status
Question: Does the relationship betweeen perceived racism and medical mistrust during COVID depend on levels of promotion of mistrust in a sample of ethnic minority youth?

data cleaning: center variables and create an interaction term
```{r}
data$RacTot_12c <- (data$RacTot_12 - 0.5333)
data$incometopovertyratio_12c <- (data$incometopovertyratio_12 - 2.25120)
data$xpromotionofmistrust_12c <- (data$xpromotionofmistrust_12 - 0.1592)
```

analyze data:
Question: Does the relationship betweeen perceived racism and medical mistrust during COVID depend on levels of preparation for bias in a sample of ethnic minority youth?

Correlations among study variables
```{r}
cor.test(data$RacTot_12c, data$xpromotionofmistrust_12c)
cor.test(data$RacTot_12c, data$xmisttrusttot_C)
cor.test(data$xpromotionofmistrust_12c, data$xmisttrusttot_C)
```

Multiple regression 
```{r}
summary(lm(xmisttrusttot_C ~  RacTot_12c*xpromotionofmistrust_12c + ChildSex + ChildRace_Final+ incometopovertyratio_12c, data=data))
```
the interaction is marginally significant

Graph
```{r}
sd(data$xpromotionofmistrust_12c, na.rm = TRUE)
sd(data$RacTot_12c, na.rm=TRUE)
```

```{r}
#Create a factor of the xpromotionofmistrust_12c variable used in the interaction  
data$xpromotionofmistrust_12f <- cut(data$xpromotionofmistrust_12c,
                      breaks=c(-Inf,-0.4782476, 0.4782476, Inf),
                      labels=c("Low levels of promotion of mistrust", "Mean promotion of mistrust", "High levels of promotion of mistrust Mean"), na.rm = TRUE)

                     
#Create a factor of the RacTot_12c variable used in the interaction 
data$RacTot_12f <- cut(data$RacTot_12c,
                      breaks=c(-Inf,-0.9910166, 0.9910166, Inf),
                      labels=c("Low levels of perceived racism", "Mean perceived racism", "High levels of perceived racism"), na.rm = TRUE)

levels(data$xpromotionofmistrust_12f)
levels(data$RacTot_12f)
```


```{r}
library(ggplot2)

data.clean<- na.omit(subset(data, select = c(xpromotionofmistrust_12f, xmisttrusttot_C, RacTot_12f)))

graph <-ggplot(data=data.clean, aes(x=xpromotionofmistrust_12f, y=xmisttrusttot_C, group=RacTot_12f))+
    geom_line(size=2, aes(color=RacTot_12f))+
    ylab("Medical Mistrust")+
    xlab("Promotion of Mistrust")+
    ggtitle("Promotion of Mistrust and Perceived Racism as Predictors of Medical Mistrust During COVID")+
    theme_bw()+
    theme(text = element_text(size=12),
        legend.text = element_text(size=12),
        legend.direction = "horizontal",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position="top")

graph

```

